Biden Projected to Win in the 2024 US Presidential Election

### 2024-03-15 paper/paper.qmd
made changes to the introduction section

# Introduction
A key turning point in the political environment of the United States occurred with the 2020 presidential election, which was marked by extreme conflict and serious economic and social challenges. We analyze data from the American Community Survey (ACS) 2022 sample, which offers a thorough understanding of demographic, socioeconomic, and geographic aspects across the nation, in order to comprehend the patterns underlying voting choices during this 2024 election period.

>>>>

# Introduction
A key turning point in the political environment of the United States occurred with the 2020 presidential election,
which was marked by extreme conflict and serious economic and social challenges. We analyze data from the American
Community Survey (ACS) 2022 sample, which offers a thorough understanding of demographic, socioeconomic,
and geographic aspects across the nation, in order to comprehend the patterns underlying voting choices during
this 2024 election period. This paper focuses on the two major political parties, Democratic and Republican.

The rivalry between the Democratic and Republican parties, as embodied by their opposing candidates,
Joe Biden and Donald Trump, has been an iconic feature of the modern American political scene. The Democratic Party's
nominee is the veteran politician and former Obama vice president Joe Biden. With an emphasis on middle-class families,
Biden's program prioritizes measures that advance racial justice, healthcare reform, climate action, and economic
regeneration. He is an advocate of a more compassionate and inclusive style of governing, hoping to bring the
country back together and bring decorum back into political conversation.

On the other hand, the current Republican Party standard-bearer and President Donald Trump represents a more populist
and nationalist agenda. A major focus on economic nationalism, immigration restrictions, tax cuts, and
deregulation have been highlights of Trump's leadership. His administration prioritized themes like law and order,
trade protectionism, and border security as part of its conservative agenda. Trump's aggressive approach to politics
is a defining characteristic of his leadership style; it frequently divides public opinion and provokes strong emotions
from both supporters and opponents.
